---
title: "MatsuokaDistribution"
output: rmarkdown::html_vignette
description: Learn how to use "MatsuokaDistribution" class object to estimate the production frontier
vignette: >
  %\VignetteIndexEntry{MatsuokaDistribution}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}

---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Summary

In this vignette there will be shown cases of use of `matsuoka.frontier` package usage

1. Pre-mounted `g(.)` estimation methods
2. Method with specific arguments
3. Method with custom `g(.)` estimative
4. Without using the wrapper `matsuoka3step`

## Setup for package use

```{r setup}
devtools::load_all()
library(matsuoka.frontier)
library(ggplot2)
library(Benchmarking)

data(milkProd)

N=nrow(milkProd)                #N=108
nc=milkProd$cows                #n cows
xc1=milkProd$vet/nc             #vet. expenses per cow (X)
x1=(xc1-min(xc1))/(max(xc1)-min(xc1))   #normalization 
xc2=milkProd$energy/nc          #energy expenses per cow (X)
x2=(xc2-min(xc2))/(max(xc2)-min(xc2))   #normalization
X=cbind(x1,x2)

y <- milkProd$milk/nc/10^3 
```

## Pre-mounted `g(.)` estimation methods

```{r premounted}
x.df <- as.data.frame(X)
res <- matsuoka.frontier::matsuoka3step(x = x.df, y = y, g = "gam")
```

This generates the `matsuoka3step` class object.
Please Check the documentation for more infomation with `help(matsuoka3step)`.

The default non-parametric function that estimates `g(.)` is set to the `gam` function.
It's possible to diagnose the `g(.)` function estimation through hierarchical built-in functions.

For example, the diagnose the default parameter `g(.)` function estimation can be done using `summary` and `plot`. This works, because `gam` has this built-in in it's class.

For example:
```{r gam diagnose}
summary(
  res$g_hat$fn_obj
)

plot(
  res$g_hat$fn_obj
)
```

After diagnosing the `g(.)` function, we can forward to the production frontier estimation diagnostics.
There is a built-in plot function that can be used, for example:
```{r gam mat}
plot(res)
plot(res, ngrid = 200, counter_levels = 15)
plot(res, ngrid = 300, counter_levels = 8, xlab = "vet/cow", ylab = "energy/cow")
```

And also a summary built-in function that provides further insights on the estimation, such as efficiency scores and percentage of efficiency stoces higher than one...
```{r}
summary(res)
```

## Method with specific arguments

## Method with custom `g(.)` estimative

## Without using the wrapper `matsuoka3step`